%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Freeman Curriculum Vitae
% XeLaTeX Template
% Version 3.0 (September 3, 2021)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Vel (vel@LaTeXTemplates.com)
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%!TEX program = xelatex
% NOTE: this template must be compiled with XeLaTeX rather than PDFLaTeX
% due to the custom fonts used. The line above should ensure this happens
% automatically, but if it doesn't, your LaTeX editor should have a simple toggle
% to switch to using XeLaTeX.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TODO: Make headings Roboto and body Roboto-serif

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	10pt, % Default font size, can be between 8pt and 12pt
]{FreemanCV}

\columnratio{0.60, 0.40} % Widths of the two columns, specified here as a ratio summing to 1 to correspond to percentages; adjust as needed for your content 

% Headers and footers can be added with the following commands: \lhead{}, \rhead{}, \lfoot{} and \rfoot{}
% Example right footer:
%\rfoot{\textcolor{headings}{\sffamily Last update: \today. Typeset with Xe\LaTeX}}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND CURRICULUM VITAE TITLE
%----------------------------------------------------------------------------------------
	
{\sffamily\Huge\noindent Conor Masterson} % Your name
	
\medskip % Vertical whitespace
	
{\noindent Senior Software Engineer with over 10 years of experience in software development, team leadership, and project management. Expertise in Swift, Objective-C and C\#. A proven track record with high-profile clients \\including Unum, Mozilla and Intuit.}
\medskip

\begin{paracol}{2} % Begin two-column mode

%--------------------------------------------------------------------------
%	WORK EXPERIENCE
%--------------------------------------------------------------------------

\jobentry
	{Senior Software Engineer - Mozilla}
    {March 2023 - Feb 2024 | Canada (Remote)}
    {At Mozilla, I played a pivotal role in the adoption of \\Application Services and its integrations by building \\prototypes, creating or enhancing necessary documentation, and organizing meetings with key stakeholders. I also \\developed modules essential to the Social experience and took initiative during uncertain times to build a proof-of-concept app and bring it to market quickly and cost-effectively. Key contributions include:\medskip\\
    • Built and enhanced prototypes to support Application \\Services adoption.\\
    • Improved and created documentation for better integration and stakeholder understanding.\\
    • Organized and led meetings with key stakeholders to drive project success.\\
    • Developed crucial modules for the Mozilla Social experience.\\
    • Built a proof-of-concept app efficiently in challenging \\circumstances.}

%------------------------------------------------

\jobentry
	{Senior Software Engineer - Intuit}
	{June 2020 - Aug 2022}
	{As the team lead for TurboTax iOS, I fostered a positive \\culture through open communication, social activities, \\routine check-ins, and mentoring. I contributed to the \\architecture of the modular codebase for the TurboTax \\Platform and assisted the Technical Manager with goal \\setting and planning. Key achievements include:\medskip\\
    • Modernized legacy code, reducing tech debt and enhancing testing.\\
    • Improved Agile processes and rituals within the team.\\
    • Developed comprehensive on-boarding and off-boarding \\documentation.\\
    • Coordinated with teams to adopt Platform modules.\\
    • Authored technical retrospectives and team improvement plans.}

%------------------------------------------------

\jobentry
	{Software Engineer - TouchBistro}
    {July 2019 - June 2020}
    {At TouchBistro, I improved payment terminal integrations and maintained high testing standards using Quick/Nimble. I led the standardization of UI components with TBUIKit, ensuring reliability and ease of implementation. Additionally, I \\introduced new processes, testing, and documentation \\methodologies to enhance TBUIKit.}

%------------------------------------------------

\jobentry
    {Senior Software Engineer - Clearbridge Mobile}
    {October 2017 - July 2019}
    {At Clearbridge, I worked as a consultant, delivering rapid \\solutions and expertise to various companies. Key projects included:\medskip\\
    • Spearheaded the rebuild of Bell Media’s Crave app for iOS and AppleTV.\\
    • Developed the International Transfer module for TD Bank.\\
    • Enhanced Chatr’s Client app and NBC Sports’ iOS app.}

%------------------------------------------------

\jobentry
    {Software Engineer - Marino Software}
    {April 2013 - July 2019}
    {At Marino Software, I developed new games and experiences for the Curious George franchise using UIKit, crafted games using Cocos2DX with C++ for the RTE Junior app, and added functionality to the Lottery.ie app.}

%------------------------------------------------

\jobentry
    {Programmer Analyst - Unum Ireland}
    {October 2010 - April 2013}
    {At Unum Ireland, I worked on the UnumBenefits.com web \\portal, utilizing C\# and ASP.NET to build new features and resolve issues.}
    
%----------------------------------------------------------------------------------------

\switchcolumn % Switch to the second (right) column

%----------------------------------------------------------------------------------------
%	COLORED CONTACT DETAILS BOX
%----------------------------------------------------------------------------------------
\section{Contact} 
\begin{tabular}{c | l}
    {\faPhone} & +1 (647) 705-9157 \\ % Phone number
	{\small\faEnvelope} & \href{mailto:cdamasterson@gmail.com}{cdamasterson@gmail.com} \\ % Email address, standard icon is too large.
	{\faGithub} & \href{https://github.com/CMasterson}{CMasterson} \\ % Website
	{\faLinkedinSquare} & \href{https://www.linkedin.com/in/conor-masterson/}{conor-masterson} \\ % LinkedIn profile
    {\faMapMarker} & Toronto, Ontario. CA. \\ % Address
\end{tabular}
\medskip

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\section{Skills}
\begin{table}[h]
\resizebox{\columnwidth}{!}{
    \begin{tabular}{lll}
        Swift   & Objective-C     & C\#          \\
        UIKit   & SwiftUI         & Async/Await  \\
        Testing & Version Control & Architecture \\
        REST    & Team Dynamics   & Databases   
    \end{tabular}
}
\end{table}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education} 
B.Sc (Hons) Computer Games \\Development
\medskip

%----------------------------------------------------------------------------------------
%	Hobbies & Interests
%----------------------------------------------------------------------------------------

\section{Hobbies \& Interests}
\subsection{Coding}
I enjoy experimenting with programming languages and developing tools in Python to assist friends and family. I have built a replica of the WWII Enigma encryption machine using Golang, brought a statue to life with Arduino for Nuit Blanche, and am currently teaching myself Unity with C\# to create simple games.\\Most recently, I learned \LaTeX to create this resume.

\subsection{Makerspace}
As the Chair of the Board of Directors for a Toronto makerspace, I volunteer my time to ensure members have a safe and \\creative space to work and learn. We \\support various disciplines and offer classes to the public.

\subsection{Climbing}
Introduced to bouldering by a co-op, I now visit the climbing gym at least once a week. I love the blend of physical challenge and problem-solving that climbing offers.

\subsection{Outdoors}
When the weather is favorable, my \\partner and I visit Seaton Park for \\outdoor archery. We also hike in the \\Escarpment and go on portaging trips with friends in Algonquin Park.

\subsection{Gaming}
In my downtime, I enjoy both new releases and classic video games. Weekly, I gather with friends for tabletop games and \\regularly participate in and occasionally run D\&D 5e campaigns.

%----------------------------------------------------------------------------------------

\end{paracol} % End two-column mode

%----------------------------------------------------------------------------------------

\end{document}
